\subsection{Bottom hatch}
The bottom hatch, localized at the bottom of the arc chamber, has 80 cm
diameter, enabling mid-sized robots entry, but it is 10 m far from the blade,
requiring system transportation and positioning. Using the bottom hatch as the
access for robot has the follwing advantages: large enough for medium sized
robots, free access, it is normally used by operators to turbine maintenance.
And the following disadvantages: not large enough for large robots, complex
logistics to the hatch (scaffolding and hoists), difficulty for robot moving
and positioning in the arc chamber due to the slippery and sloping floor.

%Solutions for the bottom hatch have the following advantages and
%disadvantages:
%Soluções que utilizem o acesso pela escotilha inferior, de dimensão maior,
%apresentam as seguintes vantagens e desvantagens:

%\textbf{Advantages}:
%\begin{itemize}
%  \item large enough for medium sized robots
%  \item free access
%  \item it is normally used by operators to turbine maintenance.
%\end{itemize}

%\textbf{Disadvantages}
%\begin{itemize}
%  \item not large enough for large robots
%  \item complex logistics to the hatch. Scaffolding and hoists are
%  needed
%  \item difficulty for robot moving and positioning in the arc chamber due to
%  the slippery and sloping floor.
%\end{itemize}

The bottom hatch, like all other accesses, is a logistical challenge and
a common challenge of the metallization process. The bottom hatch has 80 mm
diameter and is 4 m above ground. The system should be carried by a hoist
manually operated, installed inside the arc chamber on scaffolding. The floor
is slippery and has a cylindrical and inclined shape.

%O acesso pela escotilha inferior apresenta, como todos os outros
%acessos, um desafio logístico e o desafio comum do processo de metalização. O
%acesso à escotilha é realizado por uma abertura de 80 mm de diâmetro e 4 m
% acima do solo, logo os equipamentos são transportados por uma talha operada manualmente,
%instalada dentro do aro câmara, em andaimes. O solo é escorregadio e, devido à
%forma cilíndrica do aro câmara, curvilíneo e inclinado.

The system solutions were focused on medium size and lightweight manipulators,
due to robot shipping, handling and positioning of the robot. And modular base
solutions, when possible. Solutions were divided into subsections in accordance
with fixation strategies: mobile robots that move on rails fixed on the blade;
climbers; industrial manipulators that move on rails fixed on the floor.

%Dessa forma, as soluções foram focadas em robôs de médio porte, peso reduzido
%devido ao transporte e às necessidades de movimentação e posicionamento do robô
%(trajeto escotilha à pá), e modular, quando possível.

%As soluções foram divididas em subseções de acordo com a fixação:
%robôs móveis que se locomovem em trilhos, robôs escaladores e manipuladores
%industriais com base fixa. 
%obs.:
%Colocar o robô entre as pás para aplicar revestimento de duas pás com uma
% instalação exige que o robô seja desmontado toda vez que a turbina for girada.
%Isso é ruim, pois após primeira aplicação a área fica de risco. Esta solução
%exige 5 movimentos no robô e 6 movimentos na turbina.

%A solução em que o robô fica atrás ou à frente exige que o robô seja
%movimentado apenas 2 vezes e a turbina fará 8 movimentos (duas voltas).

%TODO revisar todos os projetos sabendo as respostas
\input{proj_rail2}
\input{proj_climbers}
\input{proj_manipuladores} 
%\input{proj_riwea}